Interval Probability for Fuzzy Quantum Theories

### 2016-06-13 prob.tex
"Referenece\S. Bartlett, T. Rudolph, R. Spekkens, Reference frames, superselection rules, and quantum information.pdf" Added...

%%%%%
\subsection{Measuring Quantum Probabilities}
\amr{preparation fuzzy, device fuzzy, Meyer~\cite{PhysRevLett.83.3751}}

>>>>

%%%%%
\subsection{Measuring Quantum Probabilities}

Similar to the classical case, to know the quantum probability for
each event, we can apply the law of large number, and measure the
relative frequency. For example, Stern and Gerlach found a silver
atoms beam deflected in a highly inhomogeneous magnetic field~\cite{Stern1988,peres1995quantum,544199,Griffiths2003}.
Ideally, if the local field strength directs to the $z$-axis, and
all particles have the same velocity, three spots will be produced
corresponding to $\ket{0}$ and $\ket{1}$. In reality, the local
field strength cannot prefect directs to to the $z$-axis, and all
atoms come from a hot oven cannot have the same velocity. The variant
of velocity makes spots broader and more washed out so that it may
sometimes hard to decide a particle corresponding to which state\footnote{\yutsung{Citation here?}}.
Similar to Buffon's needles, this kind of fuzziness can be taken into
account by associating each quantum event with an interval-valued
probability~$\left[l,r\right]$. About the imperfect direction of
field strength, we might take it into account when we introduce the
discrete quantum theory later.

\amr{preparation fuzzy, device fuzzy, Meyer~\cite{PhysRevLett.83.3751}}
